### 2021-04-23 newvariant.tex
little change with Daniel

This study has some practical implications for analyzing the epidemiological dynamics of new variants.
First, models that assume a constant relative speed, such as standard logistic growth model, should be avoided, if possible, for characterizing the growth of new variants---the relative speed changes over time depending on epidemiological conditions.
\swp{In some cases, such as early in the spread of new variants, assuming a constant relative speed may not be a bad idea if epidemiological conditions do not change much. Such simplifying assumption can also help obtain crude estimates of relative speed. However, epidemiological conditions will change over time in response to spreading new variants, causing relative speed to change and invalidating this assumption.}
\jd{need to reconcile this with advice above about Early.}
Second, the absolute strength and speed should not be neglected in favor or relative values, and both relative and absolute values should be discussed together.
While the relative strength and speed are useful for describing the spread of new variants, the absolute values determine their spread and control.
Finally, uncertainty in generation intervals should be carefully considered.

>>>>

This study has some practical implications for analyzing the epidemiological dynamics of new variants.
First, models that assume a constant relative speed, such as standard logistic growth model, should be used with care---it is important to remember that the relative speed is expected to change with epidemiological conditions.
In some cases, such as early in the spread of new variants, assuming a constant relative speed may not be a bad idea if epidemiological conditions do not change much. Such simplifying assumption can also help obtain crude estimates of relative speed. However, epidemiological conditions will change over time in response to spreading new variants, causing relative speed to change and invalidating this assumption.
Second, the absolute strength and speed should not be neglected in favor or relative values, and both relative and absolute values should be discussed together.
While the relative strength and speed are useful for describing the spread of new variants, the absolute values determine their spread and control.
Finally, uncertainty in generation intervals should be carefully considered.
